---
title: "Los quintiles y Cris"
author: "Cristina Rodríguez-Prada"
date: "`r format(lubridate::today(), 'First created on 01.02.2023. Updated on %d de %B de %Y')`"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
  html_notebook: null
institute: CCOMS, Universidad Autónoma de Madrid
editor_options:
  markdown:
    wrap: 80
---

## Required libraries

```{r library}
library(tidyverse)
library(haven)
library(freqtables)
#install.packages("freqtables")
library(ecs.data)
library(labelled)
#install.packages("labelled")
library(stringr)
library(gridExtra)
#install.packages("gridExtra")
library(lubridate)
library(naniar)
library(stringi)
library(readstata13)
library(readxl)
library(ecs.data)
library(utf8)
#TODO: Add labels to all variables
```

## Constants on variable harmonization

*Coding of missing values:*

-   -991 specifies a variable has not been assessed in general (e.g., at this
    point of data collection), so it is missing by design.

-   -992 specifies 'refused to answer' NAs

-   -993 specifies missings (default) from data collections that actually took
    place (eg, this exact questionnaire had been assessed at this timepoint, but
    the participant did not answer for whatever reason).

```{r constants}
MISSING_DESIGN <- -991
REFUSED_ANSWER <- -992 #999 
NON_RESPONSE <- -993 #888
BASELINE_FILEPATH <- file.path(read_ecs_folder("DB"),
                               "Ola_3/Cohorte_2019/rawdata_c2019w1.dta")
COVID_FILEPATH <- file.path(read_ecs_folder("DB"), 
                        "Subestudio_COVID/Edad_con_salud_Fichero_Completo.dta")
```

## Data importation

Data is extracted from the OneDrive folders `Bases de datos maestras`. For
RESPOND WP2, the used folders are `Cohort 2019`and `COVID Substudy`. Files are
in .dta format, which is a double format. It contains:

-   the variable type (class)
-   the label (label, part of the metadata)

For ease of work, it is necessary to make variable transformations so that
`value-label` does not interfere, as it doesn't say anything about the
categorical or continuous consideration of the variables.

**Before doing the data analysis it is required to convert the vectors with**
**`value_labels`** into factors, numeric or character vectors. To do this, it is
possible to use `unlabelled()`, `to_factor()` o `unclass()` before data cleaning
or after that, to keep the info in the export process.

The original databases are then imported and copies are created for testing
purposes.

```{r data-importation}
data_2019 <- read_dta(BASELINE_FILEPATH, encoding = "UTF-8")
data_COVID <- read_dta(COVID_FILEPATH)
```

# Step 1. Data inspection

## Checking columns

We check that the variable names are correct, if there are duplicate columns and
if the column names of each wave are unique. This should be the case because of
the nature of the coding of the `Edad con Salud` inter#Views.

```{r}
raw_2019_colnames <- colnames(data_2019)
raw_COVID_colnames <- colnames(data_COVID)
```

```{r}
intersect(raw_2019_colnames, raw_COVID_colnames)
```

```{r}
print(raw_2019_colnames[duplicated(raw_2019_colnames)])
print(raw_COVID_colnames[duplicated(raw_COVID_colnames)])
```

The variables common to both datasets are `ID_ECS` and `origin`. `ID_ECS` would
be the key variable to join both datasets. There are no duplicates on each
dataset and everything looks perfectly fine on this respect.

```{r}
rm(raw_2019_colnames)
rm(raw_COVID_colnames)
```

## Checking rows

On COVID substudy there's one case that is not on baseline wave. We have to
remove it. Firstly, we detect it using anti_join():

```{r}
id_ecs_subs_notBL <- data_COVID %>%
                anti_join(data_2019, by = "ID_ECS") %>% 
                select(ID_ECS) %>% pull()
```

And then we remove it (is ID_ECS == 6900702)

```{r}
data_COVID <- data_COVID %>% 
  filter(ID_ECS != id_ecs_subs_notBL)
```

## Identifying waves

```{r}
data_2019 <- data_2019 %>%
              add_column(wave = 1, .before = "ID_ECS")
  
```

```{r}
data_COVID <- data_COVID %>%
              add_column(wave = 2, .before = "ID_ECS")
  
```

Now we duplicate both datasets for testing purposes:

```{r}
data_2019_test <- data_2019
data_COVID_test <- data_COVID
```

## Follow-up cases

In order to know what cases are in both waves, we use semi_join:

```{r}
id_ecs_both <- data_COVID_test %>%
               semi_join(data_2019_test, by = "ID_ECS") %>% 
               select(ID_ECS) %>% 
               pull()
```

## Adjusting date format

Date format is important because we are using this variables to create some of
the required variables for RESPOND WP2.

```{r dates-format}
data_2019_test <- data_2019_test %>% 
  mutate(
    q0006_date = lubridate::ymd(q0006_date),
    q1010_birth_date = lubridate::ymd(q1010_birth_date)
  )
data_COVID_test <- data_COVID %>% 
  mutate(
  FECHAFIN = lubridate::dmy(FECHAFIN)
)  
  
birthday <- data_2019_test %>% 
  mutate(
    q1010_birth_date = lubridate::ymd(q1010_birth_date)) %>% 
  select(q1010_birth_date) %>% 
  pull()
inter#View2019 <- data_2019_test %>% 
      select(q0006_date) %>% 
      pull()
inter#Viewcovid <- data_COVID_test %>% 
    select(FECHAFIN) %>% 
    pull()
  
```

# Quartiles & Quintiles

Quartiles and quintiles have to be created from baseline cohort. We'll sum all
the variables that collect data on income:

-   `q0410g_total`: gross personal income of all members of your family during
    the last 12M.
-   `q0410i_ss`: gross household income during the last 12M from the retirement
    pension.
-   `q0410j_government`: gross household income (...) from official programs
    (unemployment, dependent children, widows, widowers, orphans, general
    assistance, ...).
-   `q0410k_other`: from private sources (pensions, investments, alimony or
    maintenance).

We have to take into account:

-   The characteristics of the double format of database variables in Stata make
    it necessary to do some previous transformations to be able to handle it
    properly.

-   The NAs for each variable result in a number of NAs different from the
    number of NAs for each of these variables separately.
    

```{r}
temp <- data_2019_test %>%
  mutate(
    q0410g_total = as.factor(q0410g_total),
    q0410i_ss = as.factor(q0410i_ss),
    q0410j_government = as.factor(q0410j_government),
    q0410k_other = as.factor(q0410k_other),

    q0410g_total_rec = recode_factor(q0410g_total,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),

    q0410i_ss_rec = recode_factor(q0410i_ss,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),

    q0410j_government_rec = recode_factor(q0410j_government,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),

     q0410k_other_rec = recode_factor(q0410k_other,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid")
    ) %>% count(q0410g_total_rec,  q0410i_ss_rec, q0410j_government_rec, q0410k_other_rec)

```

```{r}
temp %>% 
  filter(if_any(everything(), `==`, "valid"))
##View(.Last.value)
```
```{r}
temp %>%
  filter(q0410g_total_rec == "valid") %>% 
  count(wt = n)
```
We assume that most of the respondents' income will be in what they answer 
in item `q0410g_total`. Therefore, if in this variable we find a "valid" 
response, in the following ones, the don't know or refuse will become 0. 

If in this variable the answer is "don't know" or "refuse", a decision will
be made for the cases depending on which type of answer has been given to a 
greater extent. Thus, if in "total":
- we have a response that is a "don't know" and we find that same response in
another variable, we classify it as "don't know" in the final sum;
- If we have an answer that is "refuse" and we find that same answer in another
variable, we classify it as "refuse" in the final sum. 

### Variable recoding

These variables are originally factor variables with a value of a number from 1
to 33 and a label indicating the median value of the established range.

We have, therefore, to convert these factor variables into numeric variables
whose values are the information of the median of the established range
(currently they are there as labels). To do this, we will:

-   recode them into the respective medians,
-   change their format,
-   change the value of the NAs to what was agreed in RESPOND,
-   convert the missing values into NAs in order to be able to do the sum,
-   sum
-   and divide by quintiles and convert the NAs into their original values.

```{r}
data_2019_test <- 
  data_2019_test %>% 
  mutate(q0410g_total_r = recode_factor(q0410g_total,
                                          "999" = REFUSED_ANSWER,
                                          "888" = NON_RESPONSE,
                                          "1"  =           0, "2"  =      0, "3"  =    500, "4"  =    1500,
                                          "5"  =        2500, "6"  =   3500, "7"  =   4500, "8"  =    5500,
                                          "9"  =        6500, "10" =   7500, "11" =   8500, "12" =    9500,
                                          "13" =       10500, "14" =  11500, "15" =  12500, "16" =   13500,
                                          "17" =       14500, "18" =  15500, "19" =  16500, "20" =   17500,
                                          "21" =       18500, "22" =  19500, "23" =  22500, "24" =   27500,
                                          "25" =       32500, "26" =  37500, "27" =  42500, "28" =   47500,
                                          "29" =       62500, "30" =  87500, "31" = 125000, "32" =  175500,
                                          "33" =      250000, "34" = 400000, "35" = 750000, "36" = 1000000),
         
         q0410i_ss_r = recode_factor(q0410i_ss,
                                          "999" = REFUSED_ANSWER,
                                          "888" = NON_RESPONSE,
                                          "1"  =           0, "2"  =      0, "3"  =    500, "4"  =    1500,
                                          "5"  =        2500, "6"  =   3500, "7"  =   4500, "8"  =    5500,
                                          "9"  =        6500, "10" =   7500, "11" =   8500, "12" =    9500,
                                          "13" =       10500, "14" =  11500, "15" =  12500, "16" =   13500,
                                          "17" =       14500, "18" =  15500, "19" =  16500, "20" =   17500,
                                          "21" =       18500, "22" =  19500, "23" =  22500, "24" =   27500,
                                          "25" =       32500, "26" =  37500, "27" =  42500, "28" =   47500,
                                          "29" =       62500, "30" =  87500, "31" = 125000, "32" =  175500,
                                          "33" =      250000, "34" = 400000, "35" = 750000, "36" = 1000000),
        q0410j_government_r = recode_factor(q0410j_government,
                                          "999" = REFUSED_ANSWER,
                                          "888" = NON_RESPONSE,
                                          "1"  =           0, "2"  =      0, "3"  =    500, "4"  =    1500,
                                          "5"  =        2500, "6"  =   3500, "7"  =   4500, "8"  =    5500,
                                          "9"  =        6500, "10" =   7500, "11" =   8500, "12" =    9500,
                                          "13" =       10500, "14" =  11500, "15" =  12500, "16" =   13500,
                                          "17" =       14500, "18" =  15500, "19" =  16500, "20" =   17500,
                                          "21" =       18500, "22" =  19500, "23" =  22500, "24" =   27500,
                                          "25" =       32500, "26" =  37500, "27" =  42500, "28" =   47500,
                                          "29" =       62500, "30" =  87500, "31" = 125000, "32" =  175500,
                                          "33" =      250000, "34" = 400000, "35" = 750000, "36" = 1000000),
        q0410k_other_r = recode_factor(q0410k_other,
                                          "999" = REFUSED_ANSWER,
                                          "888" = NON_RESPONSE, 
                                          "1"  =           0, "2"  =      0, "3"  =    500, "4"  =    1500,
                                          "5"  =        2500, "6"  =   3500, "7"  =   4500, "8"  =    5500,
                                          "9"  =        6500, "10" =   7500, "11" =   8500, "12" =    9500,
                                          "13" =       10500, "14" =  11500, "15" =  12500, "16" =   13500,
                                          "17" =       14500, "18" =  15500, "19" =  16500, "20" =   17500,
                                          "21" =       18500, "22" =  19500, "23" =  22500, "24" =   27500,
                                          "25" =       32500, "26" =  37500, "27" =  42500, "28" =   47500,
                                          "29" =       62500, "30" =  87500, "31" = 125000, "32" =  175500,
                                          "33" =      250000, "34" = 400000, "35" = 750000, "36" = 1000000)
         )
```

```{r}
data_2019_test <- 
  data_2019_test %>% 
  mutate(
        q0410g_total_r = as.character(q0410g_total_r),
        q0410i_ss_r = as.character(q0410i_ss_r),
        q0410j_government_r = as.character(q0410j_government_r),
        q0410k_other_r = as.character(q0410k_other_r),
        
        q0410g_total_r = as.integer(q0410g_total_r),
        q0410i_ss_r = as.integer(q0410i_ss_r),
        q0410j_government_r = as.integer(q0410j_government_r),
        q0410k_other_r = as.integer(q0410k_other_r)
  )
```

```{r}
data_2019_test %>%
  select(q0410g_total_r, q0410i_ss_r, q0410j_government_r, q0410k_other_r) %>%
  summarise_all(~sum(is.na(.))) #Están bien los NAs, 91 de proxy
```


```{r}
data_2019_test %>% 
  freq_table(q0410g_total_r) %>%  # 371 + 819 = 1190 NON_RESPONSE
  print(n = 26)

data_2019_test %>% 
  freq_table(q0410i_ss_r) #267 + 824 = 1091 NON_RESPONSE

data_2019_test %>% 
  freq_table(q0410j_government_r) #230 + 766 = 966 NON_RESPONSE

data_2019_test   %>% 
  freq_table(q0410k_other_r) #291 + 710 = 1001 NON_RESPONSE
```


```{r}
data_2019_test <- 
  data_2019_test %>% 
  mutate(
        q0410g_tot_NA = na_if(q0410g_total_r, NON_RESPONSE),
        q0410g_tot_NA = na_if(q0410g_tot_NA, REFUSED_ANSWER),
        q0410i_ss_NA = na_if(q0410i_ss_r, NON_RESPONSE),
        q0410i_ss_NA = na_if(q0410i_ss_NA, REFUSED_ANSWER),
        q0410j_gov_NA = na_if(q0410j_government_r, NON_RESPONSE),
        q0410j_gov_NA = na_if(q0410j_gov_NA, REFUSED_ANSWER),
        q0410k_other_NA = na_if(q0410k_other_r, NON_RESPONSE),
        q0410k_other_NA = na_if(q0410k_other_NA, REFUSED_ANSWER)
)
```

```{r}
data_2019_test %>% 
 freq_table(q0410i_ss_NA)
```

```{r}
data_2019_test %>%
  select(q0410g_tot_NA, q0410i_ss_NA, q0410j_gov_NA, q0410k_other_NA) %>%
  summarise_all(~sum(is.na(.)))
```
```{r}
data_2019_test <- 
  data_2019_test %>% 
  mutate(
    q0410g_total_factor = as.factor(q0410g_total),
    q0410i_ss_factor = as.factor(q0410i_ss),
    q0410j_government_factor = as.factor(q0410j_government),
    q0410k_other_factor = as.factor(q0410k_other),
    
    q0410g_total_rec = recode_factor(q0410g_total_factor,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),
    
    q0410i_ss_rec = recode_factor(q0410i_ss_factor,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),
    
    q0410j_government_rec = recode_factor(q0410j_government_factor,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid"),
    
     q0410k_other_rec = recode_factor(q0410k_other_factor,
      "888" = "DK",
      "999" = "refuse",
      .default = "valid")
    )
```

Las variables están en el dataset:
```{r}
data_2019_test %>% select(q0410g_total_rec:q0410k_other_rec) %>% freq_table(q0410g_total_rec:q0410k_other_rec)
```

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      q0410g_total_rec == "DK" ~ NON_RESPONSE,
                      q0410g_total_rec == "refuse" ~ REFUSED_ANSWER,
                      is.na(q0410g_total_rec) ~ NA_integer_)
  )

```
Comprobamos que las variables sirven como filtros:

```{r}
data_2019_test %>% filter(q0410g_total_rec == "valid")
data_2019_test %>% filter(q0410g_total_rec == "DK")
data_2019_test %>% filter(q0410g_total_rec == "refuse")

```

También comprobamos que la variable que queremos utilizar hasta el momento
existe y tiene categoría de integer:

```{r}
data_2019_test %>% select(q0410g_tot_NA) %>% str()
```

Si lo intentamos hacer con menos categorías:

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      TRUE ~ NA_integer_
  )
  )
```

```{r}
prueba %>% select(total) %>% freq_table(total) %>% print(n=34)
```

Esto sí funciona. Al final aquí lo podemos dejar así porque nos interesa tener
sólo los valores válidos. 

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      TRUE ~ NA_integer_
  ),
  
  pension = case_when(q0410g_total_rec == "valid" & 
                        q0410i_ss_rec == "valid" ~ q0410i_ss_NA,
                      TRUE ~ NA_integer_)
  )
```
```{r}
prueba %>% select(pension) %>% freq_table(pension) %>% print(n=34)
```

Volvemos a tener el mismo error cuando en vez de NA_integer_ lo queremos 
sustituir por un 0:

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      TRUE ~ NA_integer_
  ),
  
  pension = case_when(q0410g_total_rec == "valid" & 
                        q0410i_ss_rec == "valid" ~ q0410i_ss_NA,
                      TRUE ~ 0)
  )
```

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      TRUE ~ NA_integer_
  ),
  
  pension = case_when(q0410g_total_rec == "valid" & 
                        q0410i_ss_rec == "valid" ~ q0410i_ss_NA,
                      TRUE ~ NA_integer_),
  
  pension = coalesce(pension, 0)
  )
```

```{r}
prueba <- data_2019_test %>% 
  mutate(
    total = case_when(q0410g_total_rec == "valid" ~ q0410g_tot_NA,
                      TRUE ~ NA_integer_
  ),
  
  pension = case_when(q0410g_total_rec == "valid" & 
                        q0410i_ss_rec == "valid" ~ q0410i_ss_NA,
                      TRUE ~ NA_integer_),
  
  pension = coalesce(pension, 0),
  
  government = case_when(q0410g_total_rec == "valid" &
                    q0410j_government_rec == "valid" ~ q0410j_gov_NA,
                    TRUE ~ NA_integer_),
  
  government = coalesce(government, 0),
  
  other = case_when(q0410g_total_rec == "valid" &
                    q0410k_other_rec == "valid" ~ q0410k_other_NA,
                    TRUE ~ NA_integer_),
  other = coalesce(other, 0),
  
  hh_income_r_NA = total + pension + government + other
  
  )
```

```{r}
prueba %>% select(hh_income_r_NA) %>% freq_table(hh_income_r_NA) %>% print(n=34)
```

De esta manera obtendríamos 1281 valores perdidos, que realmente son los que no
responden de manera válida en la primera variable (total). A los que tienen
un valor válido aquí se les suma otras posibles cantidades de otros factores,
pero a los que han mostrado aquí como inválido cuentan como 0 en lo demás.
Esto puede ser una posible solución. De la otra forma, sumando todas las
variables, que muestran un distinto valor de NAs cada una, obtenemos 1087
valores perdidos en el total.

```{r}
quartiles19 <- c(9816, 15015, 22024) 
quintiles19 <- c(8847, 12997, 17422, 24104)
```

```{r}
prueba <- prueba %>% 
  mutate(
  hhquartile = case_when(
                          hh_income_r_NA <= quartiles19[1] ~ 1,
                          hh_income_r_NA > quartiles19[1] & hh_income_r_NA <= quartiles19[2] ~ 2,
                          hh_income_r_NA > quartiles19[2] & hh_income_r_NA <= quartiles19[3] ~ 3,
                          hh_income_r_NA > quartiles19[3] ~ 4,
                          is.na(hh_income_r_NA) & is.na(q0410g_total_r) & 
                                                  is.na(q0410i_ss_r) &
                                                  is.na(q0410j_government_r) &
                                                  is.na(q0410k_other_r)
                                                           ~ MISSING_DESIGN,
                          is.na(hh_income_r_NA) ~ NON_RESPONSE),   
  
  hhquartile = factor(x = hhquartile,
                          levels = c("1", "2", "3", "4", MISSING_DESIGN, NON_RESPONSE),
                          labels = c("first quartile", 
                                    "second quartile", 
                                    "third quartile", 
                                    "fourth quartile", 
                                    MISSING_DESIGN, 
                                    NON_RESPONSE)),
  
  hhquintile = case_when(
                          hh_income_r_NA <= quintiles19[1] ~ 1,
                          hh_income_r_NA > quintiles19[1] & hh_income_r_NA <= quintiles19[2] ~ 2,
                          hh_income_r_NA > quintiles19[2] & hh_income_r_NA <= quintiles19[3] ~ 3,
                          hh_income_r_NA > quintiles19[3] & hh_income_r_NA <= quintiles19[4] ~ 4,
                          hh_income_r_NA > quintiles19[4] ~ 5,
                          is.na(hh_income_r_NA) & is.na(q0410g_total_r) & 
                                                  is.na(q0410i_ss_r) &
                                                  is.na(q0410j_government_r) &
                                                  is.na(q0410k_other_r)
                                                           ~ MISSING_DESIGN,
                          is.na(hh_income_r_NA) ~ NON_RESPONSE),
  
  hhquintile = factor(x = hhquintile,
                          levels = c("1", "2", "3", "4", "5", MISSING_DESIGN, NON_RESPONSE),
                          labels = c("first quartile", 
                                    "second quartile", 
                                    "third quartile", 
                                    "fourth quartile",
                                    "fifth quintile",
                                    MISSING_DESIGN, 
                                    NON_RESPONSE))
  
  )
                          
```

### Checking new variables

```{r}
prueba %>% 
  freq_table(hhquartile)
```

```{r}
prueba %>% 
  freq_table(hhquintile)
```
Haciéndolo de la manera original (sumando todas las variables con todos los NAs,
sin recodificar) obtendríamos esta salida:

<!--  data_2019_test %>%  -->
<!-- +   freq_table(hhquartile) -->
<!-- # A tibble: 6 × 9 -->
<!--   var        cat                 n n_total percent    se t_crit   lcl   ucl -->
<!--   <chr>      <chr>           <int>   <int>   <dbl> <dbl>  <dbl> <dbl> <dbl> -->
<!-- 1 hhquartile first quartile    551    3002   18.4  0.707   1.96 17.0  19.8  -->
<!-- 2 hhquartile second quartile   310    3002   10.3  0.555   1.96  9.29 11.5  -->
<!-- 3 hhquartile third quartile    332    3002   11.1  0.573   1.96  9.99 12.2  -->
<!-- 4 hhquartile fourth quartile   722    3002   24.1  0.780   1.96 22.6  25.6  -->
<!-- 5 hhquartile -991               91    3002    3.03 0.313   1.96  2.47  3.71 -->
<!-- 6 hhquartile -993              996    3002   33.2  0.860   1.96 31.5  34.9  -->
<!-- > data_2019_test %>%  -->
<!-- +   freq_table(hhquintile) -->
<!-- # A tibble: 7 × 9 -->
<!--   var        cat                 n n_total percent    se t_crit   lcl   ucl -->
<!--   <chr>      <chr>           <int>   <int>   <dbl> <dbl>  <dbl> <dbl> <dbl> -->
<!-- 1 hhquintile first quartile    489    3002   16.3  0.674   1.96 15.0  17.7  -->
<!-- 2 hhquintile second quartile   215    3002    7.16 0.471   1.96  6.29  8.14 -->
<!-- 3 hhquintile third quartile    283    3002    9.43 0.533   1.96  8.43 10.5  -->
<!-- 4 hhquintile fourth quartile   361    3002   12.0  0.594   1.96 10.9  13.2  -->
<!-- 5 hhquintile fifth quintile    567    3002   18.9  0.714   1.96 17.5  20.3  -->
<!-- 6 hhquintile -991               91    3002    3.03 0.313   1.96  2.47  3.71 -->
<!-- 7 hhquintile -993              996    3002   33.2  0.860   1.96 31.5  34.9  -->

Haciendo la recodificación tenemos más valores perdidos, pero sabemos mejor de 
dónde vienen. 