---
title: "Dataset update checks on COVID substudy"
author: "Cristina Rodríguez-Prada"
date: "`r format(lubridate::today(), 'First created on 30 Sept. 2022. Updated on %d de %B de %Y')`"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
  html_notebook: null
institute: CCOMS, Universidad Autónoma de Madrid
editor_options:
  chunk_output_type: console
  markdown:
    wrap: 80
---

## Required libraries

```{r library}
library(tidyverse)
library(haven)
library(ecs.data)
library(haven)
library(readxl)
library(labelled)
library(glue)
library(waldo)
```

# File system constants:

## Folders:

```{r}
DATASET_FOLDER <- read_ecs_folder("DB")
SUBSTUDY_FOLDER <- file.path(DATASET_FOLDER, "Subestudio_COVID")
HISTORY_FOLDER <- file.path(SUBSTUDY_FOLDER, "Antiguas")
```

## File paths:

```{r}
RAW_DS_PATH    <- file.path(SUBSTUDY_FOLDER, "Edad_con_salud_Fichero_Completo.dta")
MOD_PATH    <- file.path("C:/Users/Cristina/Documents/workspace/Edad_con_salud_Fichero_Mod.sav")
HISTORICO_PATH <- file.path(HISTORY_FOLDER, "snapshot_2023-02-02_10-32.dta")

```

# Introduction

This document checks the updates performed on the Subestudy COVID dataset. It
compares the updated version with the latest version of the raw dataset with the
most recent modified version by Demometrica. The expected result is that both
datasets are different and matches what Eva from demometrica sended us:

CRP: *En la variable "FECHAFIN" tenemos 102 valores perdidos que no sabemos,*
*por un lado, si es información que se puede recuperar; por otro, existen*
*incongruencias con otras variables. Hay algunos casos en los que pone "cita"*
*o incluso "rechazo" en la variable "ESTADO_ENTREVISTA", lo que no debería*
*ocurrir; y hay casos que señalan "No contesta" que sí tienen datos en
FECHAFIN.* *Si los valores perdidos en FECHAFIN se deben corresponder a
entrevistas que no* *se llegaron a realizar porque no se pudo contactar con los
participantes* *no debería ocurrir nada de esto, ¿cierto?*

Eva: *Buenos días, Cristina* *He estado revisando en los ficheros que yo tenía
anteriores a este y en todos* *los casos eran contactos que se hicieron los días
29 y 30 de Junio, y alguno* *del 1 de julio, y que en estos casos no se
fusionaron los datos.* *Te he actualizado la base que tu me enviaste.* *La fecha
como bien dices, es la última vez que se hizo el contacto con el* *participante
y el resultado fue una cita, no contesta, etc.*

NOTE: This document is only a proof-of-concept, based on Dani document' that
compares the raw datasetfile with the latest historical version at the date
indicated in the document metadata (16-01-2023). The latest dataset file and
historical version backup are from 13-01-2023, 13:09.

# Dataset loading

```{r}
# Load the two datasets
#updated_dataset <- read_sav(MOD_PATH)
#original_dataset  <- read_sav(RAW_DS_PATH)

actual_dataset  <- read_stata(RAW_DS_PATH)
historico_dataset <- read_stata(HISTORICO_PATH)


```

<!-- # Checking differences -->

<!-- ## Differences in dataset attributes:  -->

```{r eval = FALSE, echo = FALSE}
original_attributes  <- original_dataset   |> attributes()
updated_attributes <- updated_dataset |> attributes()
diff_attributes    <- compare(
  original_attributes, updated_attributes,
  max_diffs   = Inf,
  x_arg       = "original",
  y_arg       = "updated",
  list_as_map = TRUE
)
```

<!-- ## Differences in variable attributes: -->

```{r eval = FALSE, echo = FALSE}
original_var_attrs  <- original_dataset   |> map(attributes)
updated_var_attrs <- updated_dataset |> map(attributes)
diff_var_attrs    <- compare(
  original_var_attrs, updated_var_attrs,
  max_diffs   = Inf,
  x_arg       = "original",
  y_arg       = "updated",
  list_as_map = TRUE
)
```

<!-- ## Differences in variable values: -->

```{r eval = FALSE, echo = FALSE}
var_names <- original_dataset |>
  select(-ID_ECS)           |>
  colnames()                |>
  set_names()

diff_values <- var_names |> imap_dfr(
  ~{
    original_var  <- original_dataset   |> select(ID_ECS, old = !!sym(.x))
    updated_var <- updated_dataset |> select(ID_ECS, new = !!sym(.x))
    
    full_join(original_var, updated_var, by = "ID_ECS")   |>
      filter((old != new) | (is.na(old) != is.na(new))) |>
      mutate(
        across(
          -ID_ECS,
          ~if (is.labelled(.)) as_factor(.) else as.character(.) |> as_factor()
        )
      )
  },
  .id = "Variable"
)
n_diff_values <- diff_values |> nrow()
```

<!-- # Differences in variable attributes: -->

```{r eval = FALSE, echo = FALSE}
diff_var_attrs
```

<!-- # Differences in values -->

```{r eval = FALSE, echo = FALSE}

print(diff_values, n = 105)
```

<!-- 105 values that were lost on `FECHAFIN` were introduced. However, there's still -->
<!-- some errors: some dates called "29/06/202" should be "29/06/2020" -->

```{r eval = FALSE, echo = FALSE}
updated_dataset <- updated_dataset %>% 
  mutate(
    FECHAFIN = recode_factor(FECHAFIN,
              "29/06/202" = "29/06/2020"
    )
  )
```

<!-- We run again the previous code until this point to check if the errors have been -->
<!-- fixed: -->

<!-- # Checking differences -->

<!-- ## Differences in dataset attributes: -->

```{r eval = FALSE, echo = FALSE}
original_attributes  <- original_dataset   |> attributes()
updated_attributes <- updated_dataset |> attributes()
diff_attributes    <- compare(
  original_attributes, updated_attributes,
  max_diffs   = Inf,
  x_arg       = "original",
  y_arg       = "updated",
  list_as_map = TRUE
)
```

<!-- ## Differences in variable attributes: -->

```{r eval = FALSE, echo = FALSE}
original_var_attrs  <- original_dataset   |> map(attributes)
updated_var_attrs <- updated_dataset |> map(attributes)
diff_var_attrs    <- compare(
  original_var_attrs, updated_var_attrs,
  max_diffs   = Inf,
  x_arg       = "original",
  y_arg       = "updated",
  list_as_map = TRUE
)
```

<!-- ## Differences in variable values: -->

```{r eval = FALSE, echo = FALSE}
var_names <- original_dataset |>
  select(-ID_ECS)           |>
  colnames()                |>
  set_names()

diff_values <- var_names |> imap_dfr(
  ~{
    original_var  <- original_dataset   |> select(ID_ECS, old = !!sym(.x))
    updated_var <- updated_dataset |> select(ID_ECS, new = !!sym(.x))
    
    full_join(original_var, updated_var, by = "ID_ECS")   |>
      filter((old != new) | (is.na(old) != is.na(new))) |>
      mutate(
        across(
          -ID_ECS,
          ~if (is.labelled(.)) as_factor(.) else as.character(.) |> as_factor()
        )
      )
  },
  .id = "Variable"
)
n_diff_values <- diff_values |> nrow()
```

<!-- # Differences in variable attributes: -->

```{r eval = FALSE, echo = FALSE}
diff_var_attrs
```

<!-- # Differences in values -->

```{r eval = FALSE, echo = FALSE}

print(diff_values, n = 105)
```

<!-- # Saving new version -->

```{r, echo = FALSE, eval = FALSE}

write_sav(updated_dataset, "C:/Users/Cristina/Documents/workspace/ECS_Substudy_Mod_CRP.sav")
```

# Checking new .dta dataset

## Checking differences

### Differences in dataset attributes:

```{r}
actual_attributes  <- actual_dataset   |> attributes()
historico_attributes <- historico_dataset |> attributes()
diff_attributes    <- compare(
  historico_attributes, actual_attributes, 
  max_diffs   = Inf,
  x_arg       = "historico",
  y_arg       = "actual",
  list_as_map = TRUE
)
```

### Differences in variable attributes:

```{r}
actual_var_attrs  <- actual_dataset   |> map(attributes)
historico_var_attrs <- historico_dataset |> map(attributes)
diff_var_attrs    <- compare(
  historico_var_attrs, actual_var_attrs, 
  max_diffs   = Inf,
  x_arg       = "historico",
  y_arg       = "actual",
  list_as_map = TRUE
)
```

### Differences in variable values:

```{r}
var_names <- historico_dataset |>
  select(-ID_ECS)           |>
  colnames()                |>
  set_names()

diff_values <- var_names |> imap_dfr(
  ~{
    historico_var  <- historico_dataset   |> select(ID_ECS, old = !!sym(.x))
    actual_var <- actual_dataset |> select(ID_ECS, new = !!sym(.x))
    
    full_join(historico_var, actual_var, by = "ID_ECS")   |>
      filter((old != new) | (is.na(old) != is.na(new))) |>
      mutate(
        across(
          -ID_ECS,
          ~if (is.labelled(.)) as_factor(.) else as.character(.) |> as_factor()
        )
      )
  },
  .id = "Variable"
)
n_diff_values <- diff_values |> nrow()
```

# Differences in variable attributes:

```{r}
diff_var_attrs
```

# Differences in values

```{r}

print(diff_values, n = 105)
```

105 values that were lost on `FECHAFIN` were introduced. However, there's still
some errors: some dates called "29/06/202" should be "29/06/2020"

```{r}
actual_dataset <- actual_dataset %>% 
  mutate(
    FECHAFIN = recode_factor(FECHAFIN,
              "29/06/202" = "29/06/2020",
    ),
    FECHAFIN = as_factor(FECHAFIN)
  )
```

We check the change we have made:

```{r}
actual_dataset %>%  select(FECHAFIN
                          ) %>% distinct() %>% print(n = 34)

```

```{r}
Edad_con_salud_Fichero_Completo <- actual_dataset
```

# Save new version:

```{r}
write_dta(actual_dataset, path = RAW_DS_PATH)
```
