---
title: "Dataset update checks on COVID substudy"
author: "Cristina Rodríguez-Prada"
date: "`r format(lubridate::today(), 'First created on 30 Sept. 2022. Updated on %d de %B de %Y')`"
output:
  html_document:
    df_print: paged
  toc: yes
  toc_float: yes
  html_notebook: null
institute: CCOMS, Universidad Autónoma de Madrid
editor_options:
  chunk_output_type: console
  markdown:
    wrap: 80
---

## Required libraries

```{r library}
library(tidyverse)
library(haven)
library(ecs.data)
library(haven)
library(readxl)
library(labelled)
library(glue)
library(waldo)
```

## File system constants:

## Folders:
```{r}
DATASET_FOLDER <- read_ecs_folder("DB")
SUBSTUDY_FOLDER <- file.path(DATASET_FOLDER, "Subestudio_COVID")
HISTORY_FOLDER <- file.path(SUBSTUDY_FOLDER, "Antiguas")
```

## File paths:
```{r}
RAW_DS_PATH    <- file.path(SUBSTUDY_FOLDER, "Edad_con_salud_Fichero_Completo.dta")
MOD_PATH    <- file.path("C:/Users/Cristina/Documents/workspace/Edad_con_salud_Fichero_Mod.dta")
BACKUP_PATH    <- file.path(HISTORY_FOLDER, "snapshot_2022-04-04_11-10.dta")
```


# Introduction
This document checks the updates performed on the Subestudy COVID dataset by 
Demometrica. It compares the updated version with the latest version of the raw 
dataset with the most recent modified version by Demometrica. 
The expected result is that both datasets are different and matches what Eva
from demometrica sended us:

CRP: *En la variable "FECHAFIN" tenemos 102 valores perdidos que no sabemos,*
*por un lado, si es información que se puede recuperar; por otro, existen*
*incongruencias con otras variables. Hay algunos casos en los que pone "cita"*
*o incluso "rechazo" en la variable "ESTADO_ENTREVISTA", lo que no debería*
*ocurrir; y hay casos que señalan "No contesta" que sí tienen datos en*
*FECHAFIN.* *Si los valores perdidos en FECHAFIN se deben corresponder a*
*entrevistas que no* *se llegaron a realizar porque no se pudo contactar con los*
*participantes* *no debería ocurrir nada de esto, ¿cierto?*

Eva: *Buenos días, Cristina* *He estado revisando en los ficheros que yo tenía*
*anteriores a este y en todos* *los casos eran contactos que se hicieron los días*
*29 y 30 de Junio, y alguno* *del 1 de julio, y que en estos casos no se*
*fusionaron los datos.* *Te he actualizado la base que tu me enviaste.* *La fecha*
*como bien dices, es la última vez que se hizo el contacto con el* *participante*
*y el resultado fue una cita, no contesta, etc.*

**NOTE**: This document is only a proof-of-concept, based on Dani document' that
compares the raw datasetfile with the latest historical version at the date
indicated in the document metadata (13-02-2023). The latest dataset file and
historical version backup are from 13-02-2023.

# Dataset loading
Files are in Stata 13, and therefore the UTF-8 encoding must be explicitly 
stated when reading the datasets into R. However, `encoding = 'UTF-8` when it 
comes to COVID subestudy gives an error: _Unable to convert string to the_
_requested encoding (invalid byte sequence)._
```{r}
#Load the three datasets
current_dataset <- read_stata(RAW_DS_PATH)
modified_dataset <- read_stata(MOD_PATH)
backup_dataset  <- read_stata(BACKUP_PATH)
```


# Checking differences with current dataset
To explore systematically these differences, we use waldo::compare():
```{r}
# Differences in dataset attributes:
current_attributes  <- current_dataset   |> attributes()
modified_attributes <- modified_dataset |> attributes()
diff_attributes    <- compare(
  current_attributes, modified_attributes,
  max_diffs   = Inf,
  x_arg       = "current",
  y_arg       = "modified",
  list_as_map = TRUE
)

# Differences in variable attributes:
current_var_attrs  <- current_dataset   |> map(attributes)
modified_var_attrs <- modified_dataset |> map(attributes)
diff_var_attrs    <- compare(
  current_var_attrs, modified_var_attrs,
  max_diffs   = Inf,
  x_arg       = "current",
  y_arg       = "modified",
  list_as_map = TRUE
)

# Differences in variable values:
var_names <- current_dataset |>
  select(-ID_ECS)           |>
  colnames()                |>
  set_names()


diff_values <- var_names |> imap_dfr(
  ~{
    current_var  <- current_dataset   |> select(ID_ECS, old = !!sym(.x))
    modified_var <- modified_dataset |> select(ID_ECS, new = !!sym(.x))
    
    full_join(current_var, modified_var, by = "ID_ECS")   |>
      mutate(
        old = as.character(old),
        new = as.character(new)
      ) |> 
      filter((old != new) | (is.na(old) != is.na(new))) |>
      mutate(
        across(
          -ID_ECS,
          ~if (is.labelled(.)) as_factor(.) else as.character(.) |> as_factor()
        )
      )
  },
  .id = "Variable"
)
n_diff_values <- diff_values |> nrow()
```

## Differences in values
```{r}
diff_values
```

## Differences in variable attributes
```{r}
diff_var_attrs
```


# Checking differences with backup dataset
To explore systematically these differences, we use waldo::compare():
```{r}
# Differences in dataset attributes:
backup_attributes  <- backup_dataset   |> attributes()
modified_attributes <- modified_dataset |> attributes()
diff_attributes    <- compare(
  backup_attributes, modified_attributes,
  max_diffs   = Inf,
  x_arg       = "backup",
  y_arg       = "modified",
  list_as_map = TRUE
)

# Differences in variable attributes:
backup_var_attrs  <- backup_dataset   |> map(attributes)
modified_var_attrs <- modified_dataset |> map(attributes)
diff_var_attrs    <- compare(
  backup_var_attrs, modified_var_attrs,
  max_diffs   = Inf,
  x_arg       = "backup",
  y_arg       = "modified",
  list_as_map = TRUE
)

# Differences in variable values:
var_names <- backup_dataset |>
  select(-ID_ECS)           |>
  colnames()                |>
  set_names()


diff_values <- var_names |> imap_dfr(
  ~{
    backup_var  <- backup_dataset   |> select(ID_ECS, old = !!sym(.x))
    modified_var <- modified_dataset |> select(ID_ECS, new = !!sym(.x))
    
    full_join(backup_var, modified_var, by = "ID_ECS")   |>
        mutate(
        old = as.character(old),
        new = as.character(new)
      ) |> 
      filter((old != new) | (is.na(old) != is.na(new))) |>
      mutate(
        across(
          -ID_ECS,
          ~if (is.labelled(.)) as_factor(.) else as.character(.) |> as_factor()
        )
      )
  },
  .id = "Variable"
)
n_diff_values <- diff_values |> nrow()
```

## Differences in values
```{r}
diff_values
```

## Differences in variable attributes
```{r}
diff_var_attrs
```


# Problem solving
```{r}
modified_dataset |>
  select(FECHAFIN) |>  
  mutate(FECHAFIN = sjlabelled::as_label(FECHAFIN)) |> 
  freqtables::freq_table(FECHAFIN) |> 
  print(n = 50)
```

```{r}
modified_dataset <- modified_dataset |>
  mutate(FECHAFIN = sjlabelled::as_label(FECHAFIN),
         FECHAFIN = as.character(FECHAFIN),
         FECHAFIN = lubridate::dmy(FECHAFIN))
```

```{r}
modified_dataset |> select(FECHAFIN) |> str()
```

```{r}
write_dta(modified_dataset, path = "C:/Users/Cristina/Documents/workspace/prueba-fecha.dta", version = 13L)
```

```{r}
prueba_fecha <- read_dta("C:/Users/Cristina/Documents/workspace/prueba-fecha.dta", encoding = "UTF-8")
```


